Efficiently Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-14 robdml.tex
tex

Given an anchor image $X_a$, we sample a positive image $X_p^S$ (in the same
class as the anchor) and a negative image $X_n^S$ (in different class as the
anchor) with a certain sampling strategy (\eg, semi-hard~\cite{facenet}).
%
% For convenience we call this triplet as ``source triplet''.
%
Then its \emph{hardness} is defined as
$H(X_a,X_p^S,X_n^S)=d_\phi(X_a,X_p^S)-d_\phi(X_a,X_n^S)$, which is an internal
part of the triplet loss.
%
For convenience we call this as ``source hardness'', denoted as $H_S$.

@@

@@

In literature, various triplet sampling strategies exist, such as random,
semihard~\cite{facenet}, softhard~\cite{revisiting}, distance~\cite{distance},
and the hardest negative sampling (\ie, the negative sample with the largest
loss value).
%
Although any of them can be selected for source or destination hardness for HM,
not all the possible combinations are expected to be effective or efficient.
%
In order to figure out an empirically good combination of source and
destination hardness, we adversarially train RN18 models on the CUB dataset
with every possible combination, and compare their R@1 and ERS performance in
\cref{tab:desth}.
%
Note, these methods are empirically sorted by their expectation of hardness
$E[H]$, in the ascending order: random, semihard, softhard, distance, and
hardest.
%
\oo{todo: table of first and second order central moment}

>>>>

Given an anchor image $X_a$, we sample a positive image $X_p^S$ (in the same
class as the anchor) and a negative image $X_n^S$ (in different class as the
anchor) with a certain sampling strategy (\eg, semi-hard~\cite{facenet}).
%
% For convenience we call this triplet as ``source triplet''.
%
Then its \emph{hardness} is defined as
%
\begin{equation}
%
H(X_a^S,X_p^S,X_n^S)=d_\phi(X_a,X_p^S)-d_\phi(X_a,X_n^S),
%
\end{equation}
%
which is an internal
part of the triplet loss.
%
For convenience we call this as ``source hardness'', denoted as $H_S$.

@@

\input{tab-hsort.tex}

@@

In literature, various triplet sampling strategies exist, such as random,
semihard~\cite{facenet}, softhard~\cite{revisiting}, distance~\cite{distance},
and the hardest negative sampling (\ie, the negative sample with the largest
loss value).
%
Although any of them can be selected for source or destination hardness for HM,
not all the possible combinations are expected to be effective or efficient.
%
In order to figure out an empirically good combination of source and
destination hardness, we adversarially train RN18 models on the CUB dataset
with every possible combination, and compare their R@1 and ERS performance in
\cref{tab:desth}.
%
Note, these methods are empirically sorted by their expectation of hardness
$E[H]$, in the ascending order: random, semihard, softhard, distance, and
hardest, as shown in \cref{tab:hsort}.
